Iterative construction of replicated designs based on Sobol' sequences

### 2016-06-29 crass/crassnew.tex
Adding a little more explanatio in section 3.1 (CRASS)

Two replicated point sets of order 1, $\mathcal{P}_\ell$ and $\mathcal{P}'_\ell$, can be constructed using two $s$-dimensional Sobol' sequences. We note $C_1,\dots,C_s$ the generating matrices used to generate $\mathcal{P}_\ell$ and ${C'}_1,\dots,{C'}_s$ those used to generate $\mathcal{P}'_\ell$. To ensure that the $2$-dimensional projections between $\mathcal{P}_\ell$ and $\mathcal{P}'_\ell$ are as uniform as possible, these generating matrices need to be different from each other. Our choice of generating matrices $C_1,\dots,C_s,{C'}_1,\dots,{C'}_s$ is based on the results obtained by Joe and Kuo in \cite{Kuo}. 
\bigskip

>>>>

Two replicated point sets of order 1, $\mathcal{P}_\ell$ and $\mathcal{P}'_\ell$, can be constructed using two $s$-dimensional Sobol' sequences. We note $C_1,\dots,C_s$ the generating matrices used to generate $\mathcal{P}_\ell$ and ${C'}_1,\dots,{C'}_s$ those used to generate $\mathcal{P}'_\ell$. To ensure that $\mathcal{P}_\ell$ and $\mathcal{P}'_\ell$ are as uniform as possible, these generating matrices need to be different from each other. We choose $C_1,\dots,C_s,{C'}_1,\dots,{C'}_s$ to be the first $2s$ generating matrices suggested by Joe and Kuo in \cite{Kuo}, where they minimized the $t$-value for all $2$ dimensional projections.
\bigskip
